Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-26 wearables_survey.tex
Intro less rough done!

\section{Introduction}
(REDO) Basically a longer version of the abstract, plus some additional motivational things thrown in here. I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong. Hmm. Think about what to put here.

A huge paragraph or two on why wearables are important and how much they are in use. Basically, prove that the study is worth doing in the first place. Some sources to use: 2014 is year of wearables \cite{Forbes}. A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables \cite{Neilsen} says that most popular devices (61\%), followed by smart watches (45\%) and mHealth (mobile health) devices (17\%). It is estimated that ~15\% use it in daily life \cite{Nilsen}\cite{WearableStatNews}.

People are getting upset and scared about the things that can happen with wearble devices. There was a scandal with fitbit where the 1) profiles were default public and 2) sex counted as an exercise (cite that), how google had to disable facial recognition for glass (cite) along with using voice commands rather than other commands for bystanders to be informed of what is going on (cite). We suspect that there will only be more and more situations like this to come, as wearables get increasingly powerful (cite) and are getting adopted by more people (cite), and across other demographics (cite).

End this section with an explicit list of contributions made by this paper. \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item we got people's perception on various new threats for wearable devices, a wide range of threats.
\item we found out what matters in their perception of these things--data type, data recipient, and device type and how much each of those matter. We have a cool regression model for that. 
\item we found out how people's perception of threats change when it is with respect to other people consuming the data, or just the device (data type analysis ranking with appserver only verse everyone else). 
\item we got people's risk and benefit assessment of new technologies and capabilities. Most new capabilities are seen as low risk low benefit, but we suspect it's because people aren't familiar. 
\item we found out what people were, nebulously, most concerned with. Privacy, then security, health, finances, social norms. 
\item we calibrate our work so it's relevant and understandable with smartphone research and risk perception research. We can even say that we extended those areas too, if I want to be bold. 
\end{itemize}

@@

``We would like to ask you to rate the benefits associated with each of the following technologies.

Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on. (e.g. for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.

Do not consider the costs or risks associated with these items. It is true, for example, that sometimes swimmers can drown. But evaluating such risks is not your present job. Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.

@@

``We would like to ask you to rate the risks associated with each of the following technologies.

Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations. (e.g. for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.

Do not consider the costs or benefits associated with these items. It is true, for example, that electricity also creates a market for home appliances. But evaluating such benefits is not your present job. Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.

>>>>

\section{Introduction}
Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing to healthier living through fitness tracking. Wearable devices, or wearables, are the new front of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user. Wearbles are gaining lots of attention: Forbes has named 2014 the ``Year of Wearable Technology, \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.

More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}. It is estimated that 20\% the general population owns at least one wearable and 10\% uses at least one wearable in their daily lives \cite{WearableStatNews}. The demographics of wearables consumers are young and rich--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year. However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.

 %Most AR systems use voice as input \cite{roesner2014security},  along with using voice commands rather than other commands for bystanders to be informed of what is going on \cite{StarnerSpeech} but this might change since the interface needs to change.

Even in early adoption, security and privacy concerns regarding wearable devices are becoming heightened as companies make headlines for incidents resulting in users' sexual activities exposed to the public. This occured when Fitbit's fitness profiles were public by default and allowed users to track sex as an exercise\cite{Fitbit}. In other instances, public discomfort prevented certain capabilities from being enabled. Google's Glass had to disable facial recognition for Glass \cite{GlassDetection} upon release. To avoid both scandalous breaches of privacy and public opposition for new capabilities, it is critical that we understand the threat landscape for wearable devices and which issues users most care about--before wearbles get increasingly more ubiquitous and powerful \cite{Implants}. In this work, we contribute the following: \\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We show users' perceptions of a wide range of wearables threats. We contribute a topmost and bottommost concerns , along with an evaluation of which factors contribute to the severity of a threat. We find that data type, data recipient, and device type matter A\%, B\%, C\%, respectively. See section <todo> for details.  
\item We investigate how people's privacy preferences differ when data is perceived to be shared with people or a server.
\item We show risk and benefit assessments of new technologies and capabilities; most are seen as low risk low benefit, but we hypothesize this is  the result of limited exposure. 
\item We report people's self-reported top concerns for wearable devices. Privacy, by far, is the top concern. Other notable risks include information security, long-term health risks from use, finances, and change in social norms. 
\end{itemize}

@@

BENEFIT prompt:

``We would like to ask you to rate the benefits associated with each of the following technologies.  \\[-.6cm]

Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on. (e.g. for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits. \\[-.6cm]

Do not consider the costs or risks associated with these items. It is true, for example, that sometimes swimmers can drown. But evaluating such risks is not your present job. Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out. \\[-.6cm]

@@

RISK prompt:

``We would like to ask you to rate the risks associated with each of the following technologies. \\[-.6cm]

Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations. (e.g. for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks. \\[-.6cm]

Do not consider the costs or benefits associated with these items. It is true, for example, that electricity also creates a market for home appliances. But evaluating such benefits is not your present job. Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.\\[-.6cm]
